Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-03 paper/paper.qmd
adding table of contents to paper

---
title: "Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory"
subtitle: A Bayesian Analysis of Polling Data from Key Battleground States"
author: 
  - Jimin Lee
  - Sarah Ding
  - Xiyan Chen
thanks: "Code and data are available at: [https://github.com/jamiejiminlee/2024_US_Elections.git](https://github.com/jamiejiminlee/2024_US_Elections.git)."
date: today
date-format: long
abstract: "This paper presents a predictive model for the 2024 United States Presidential Election, focusing on critical battleground states. Utilizing a Bayesian approach with state-level polling data, we estimate the winning probabilities for candidates Donald Trump and Kamala Harris. Our findings reveal that Harris is projected to win in six out of seven key battleground states, including Michigan, Nevada, and North Carolina, with predicted winning percentages surpassing 50%. Given this significant advantage, we predict Kamala Harris to be the likely winner of the election. This analysis underscores the importance of battleground states in shaping electoral outcomes and provides valuable insights into voter sentiment as Election Day approaches."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory"
subtitle: A Bayesian Analysis of Polling Data from Key Battleground States"
author: 
  - Jimin Lee
  - Sarah Ding
  - Xiyan Chen
thanks: "Code and data are available at: [https://github.com/jamiejiminlee/2024_US_Elections.git](https://github.com/jamiejiminlee/2024_US_Elections.git)."
date: today
date-format: long
abstract: "This paper presents a predictive model for the 2024 United States Presidential Election, focusing on critical battleground states. Utilizing a Bayesian approach with state-level polling data, we estimate the winning probabilities for candidates Donald Trump and Kamala Harris. Our findings reveal that Harris is projected to win in six out of seven key battleground states, including Michigan, Nevada, and North Carolina, with predicted winning percentages surpassing 50%. Given this significant advantage, we predict Kamala Harris to be the likely winner of the election. This analysis underscores the importance of battleground states in shaping electoral outcomes and provides valuable insights into voter sentiment as Election Day approaches."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
